Composition-climate paper

### 2015-05-14 Composition_Ecology.Rmd
Changed plots for the climate boxplots, added some plotting changes for the hellinger distance plots, and added an ordination plot.  I'm still not super happy about the ordination plot, but it's better.

source('overlapping_distributions.R')

@@

ggplot(all.hellinger, aes(x = fixedv_c, y = fixedc_v, color = climate)) +
  geom_point(size = 2) + 
  geom_abline(intercept=0, slope = 1) + 
  facet_grid(shift ~ climate) +
  xlab('Vegetation Fixed - Climate Shifting') +
  ylab('Climate Fixed - Vegetation Shifting') +
  theme_bw() +
  theme(axis.text = element_text(family = 'serif', size = 12),
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face='bold', size = 14),
        legend.title = element_text(family = 'serif', face='bold', size = 14))

@@

```{r densityplots, warning=FALSE, message=FALSE, echo=FALSE, fig.height = 10, fig.width=7}
source('R/figures//climate_boxplots.R')

>>>>

source('R/figures//climate_boxplots.R')

@@

hell.plot

@@

```{r densityplots, warning=FALSE, message=FALSE, echo=FALSE, fig.height = 10, fig.width=7}

source('R/figures//ordination_plot.R')
ordi_plot
